Formalizing Stack Safety as a Security Property

### 2021-10-01 submission4/main.tex
Appendix labels

Most enforcement mechanisms make assumptions about their initial conditions,
so we assume that any given machine will restrict its conditions a ``well-formedness''
criterion on initial states, ensuring that they are set up properly. In the case of
Roessler and DeHon's \cite{DBLP:conf/sp/RoesslerD18}'s micro-policies, well-formedness
requires that all annotated instructions will be situated at the appropriate instruction
of a {\em blessed sequence} -- a series of instructions that are tagged to enforce correct
behavior. It can then failstop if it would
execute the blessed sequence out of order.

@@

Our model is flexible enough to support many realistic uses of the stack.
We intentionally say little or nothing about other structures
such as the heap.  Heap safety has already been studied, in isolation,
by Azevedo de Amorim et al.~\cite{DBLP:conf/post/AmorimHP18}, and we expect that their correctness condition and ours can be
combined cleanly to characterize correct protection of stack + heap.

@@

\paragraphx{Protecting the Stack with Micro-Policies}
%
\apt{Could probably condense/omit this.}
Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18}
study the protection of stack data through three families of
micro-policies that tag stack objects with a pair of frame and object identifiers
used to validate accesses: {\em Return Address Protection} (which
prevents an adversary from overwriting designated return addresses), {\em Static
Authorities} (which only allows the code of a function to access the stack frames
of its own dynamic instances), and {\em Depth Isolation}
(\cref{sec:enforcement}). All these policies exploit various kinds of spatial and
temporal locality of stack memory and local call graphs, as well as information
generated by the compilation toolchain, to strike various balances between
precision and cacheability, evaluated through benchmarks that demonstrate
limited performance overhead. In addition to the baseline ``eager'' policies,
they propose a number of lazy optimizations, notably {\em Lazy Tagging} and
{\em Lazy
Clearing} (\cref{sec:lazy}).

@@

%% Appendix
\appendix
\paragraph*{Formalization of Callee-saves Registers}
\label{app:calleesave}
%
\[\begin{split}
\codemap \in \CODEMAPS ::= & \WORDS \rightharpoonup \callmap(S)\\
\mbox{\rm{where}} ~ & S \in \REGS \rightarrow (\unsaved + \saved) \\
\end{split}\]

@@

\paragraph*{Formalization of variable passing.}
\ref{app:argpass}

@@

>>>>

Most enforcement mechanisms make assumptions about their initial conditions,
so we assume that any given machine will restrict its conditions a ``well-formedness''
criterion on initial states, ensuring that they are set up properly. In the case of
Roessler and DeHon's \cite{DBLP:conf/sp/RoesslerD18}'s micro-policies, well-formedness
requires that all annotated instructions will be situated at the appropriate instruction
of a {\em blessed sequence} --- a series of instructions that are tagged to enforce correct
behavior. It can then failstop if it would
execute the blessed sequence out of order.

@@

Our model is flexible enough to support many realistic uses of the stack.
We intentionally say little or nothing about other structures
such as the heap.  Heap safety has been studied in isolation
by Azevedo de Amorim et al.~\cite{DBLP:conf/post/AmorimHP18}, and we expect that their correctness condition and ours can be
combined cleanly to characterize correct protection of stack + heap.

@@

\paragraphx{Protecting the Stack with Micro-Policies}
%
\apt{Could probably condense/omit this.}
Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18}
study the protection of stack data through three families of
micro-policies that tag stack objects with a pair of frame and object identifiers
used to validate accesses: {\em Return Address Protection} (which
prevents an adversary from overwriting designated return addresses), {\em Static
Authorities} (which only allows the code of a function to access the stack frames
of its own dynamic instances), and {\em Depth Isolation}
(\cref{sec:enforcement}). All these policies strike various balances between
precision and performance, evaluated through benchmarks that demonstrate
limited performance overhead. In addition to the baseline ``eager'' policies,
they propose a number of lazy optimizations, notably {\em Lazy Tagging} and
{\em Lazy
Clearing} (\cref{sec:lazy}).

@@

\pagebreak

%% Appendix
\appendices
\section{Formalization of Callee-saves Registers}
\label{app:calleesave}
%
\[\begin{split}
\codemap \in \CODEMAPS ::= & \WORDS \rightharpoonup \callmap(S)\\
\mbox{\rm{where}} ~ & S \in \REGS \rightarrow (\unsaved + \saved) \\
\end{split}\]

@@

\section{Formalization of variable passing.}
\label{app:argpass}

@@

\section{Formalization of Exceptions}
